### 2016-09-01 lineups.Rnw
code chunk facets_correct: reordering of bars not working? why?????

We collected 10 lineups each from 77 Amazon Turk users on July 28, 2016 from 19:11:03 GMT to 22:17:47 GMT. A table of demographic information collected on the participants in the experiment is in Table~\ref{fig:demos}.

@@

<<facets_correct, echo=FALSE, fig.align="center", fig.cap="Plots chosen for each of the 25 lineups in the experiment. The x-axis ticks do not have a label because the label is less important than the number of different plots users chose and whether or not they chose the correct plot, shown in the coloring of the bars.", fig.height=9>>=
ggplot(data = summ_res_wts, aes(x = as.factor(response_no2), 
                                y = tot_wt,
                                fill = correct)) + 
  geom_bar(color = 'black', stat = 'identity') + 
  scale_fill_manual(values = c("white", "grey30"), 
                    name = "Correct?") + 
  facet_wrap(~group_name, scales = "free", nrow = 5) +
  theme_bw() + 
  theme(axis.text.x = element_blank(), 
        legend.position = 'bottom') + 
  labs(x = "User Response" , y = "Number of Responses")
@

>>>>

We collected 10 lineups each from 77 Amazon Turk users. A table of demographic information collected on the participants in the experiment is in Table~\ref{fig:demos}.

@@

<<facets_correct, echo=FALSE, fig.align="center", fig.cap="Plots chosen for each of the 25 lineups in the experiment. The x-axis ticks do not have a label because the label is less important than the number of different plots users chose and whether or not they chose the correct plot, shown in the coloring of the bars.", fig.height=9>>=
ggplot(data = summ_res_wts, 
       aes(x = reorder(as.factor(response_no2), -tot_wt), 
                                y = tot_wt,
                                fill = correct)) + 
  geom_bar(color = 'black', stat = 'identity') + 
  scale_fill_manual(values = c("white", "grey30"), 
                    name = "Correct?") + 
  facet_wrap(~group_name, scales = "free", nrow = 5) +
  theme_bw() + 
  theme(legend.position = 'bottom') + 
  labs(x = "User Response" , y = "Number of Responses") 
@
